Distrivia: A Distributed Trivia Game

### 2011-04-08 papers/phase-one/paper.tex

\subsection {Messages}
We are currently using https protocol for our messages. This provides a secure
and usable messaging system that we have designed our client and server APIs to use.
The actual messages are sent and received in two way's. Initially a user session key is
genereated using the UUID \cite{uuid} algorithm and returned to the user on sucessful
authenticaton. This session key is then passed back to the server with every in coming
message. Messages are sent to the server using POST and GET request methods supported
by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
JSON is a small, easily parsable format, representing objects in a human readable format as
they would be represented in JavaScript. With the web client the JSON object returned from
the server is instantly useable, however for the android client we have to parse the JSON object
into a native java object. The Android SDK provides libraries to do this, located in the
org.json \cite{orgjson} package namespace.
\section {What's Left}
\subsection {Web Client}
 Joining/playing private games
 In-game leaderboard
 inish connecting to actual server API
 Implement useful user warnings
\subsection {Android}
So far, the only connection to the server that the android client has is when it
registers/logs in. We still need to connect the rest of the android client to
the server API to make sure all the communication between the android client
and the server are working. This includes joining public/private rounds,
competing in these rounds, and viewing leaderboards. While the UI is nearly
finished on the android client, nearly all of the connections to the servers
has yet to be done. Additionally, the android client needs to have more user
feedback and increased ability for the users to control which activity they
are in.
\subsection {Server}
Private game joining
Global leaderboard

>>>>

\subsection {Messages}
We are currently using https protocol for our messages. This provides a secure
and usable messaging system that we have designed our client and server APIs to use.
The actual messages are sent and received in two way's. Initially a user session key is
genereated using the UUID \cite{uuid} algorithm and returned to the user on sucessful
authenticaton. This session key is then passed back to the server with every in coming
message. Messages are sent to the server using POST and GET request methods supported
by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
JSON is a small, easily parsable format, representing objects in a human readable format as
they would be represented in JavaScript. With the web client the JSON object returned from
the server is instantly useable, however for the android client we have to parse the JSON object
into a native java object. The Android SDK provides libraries to do this, located in the
org.json \cite{orgjson} package namespace.
\section {What's Left}
\subsection {Web Client}
A lof of the main features of the web client are completed.
However, there are stil a few remaining features that need to be implemented.
The first is private games.
Joining them has only been stubbed out with no functionality.
The game playing routinees from public games should be compatible with private games, but may need a few tweeks as well.
Next, while it currently supports a universal leaderboard, it also needs to be able to display one ingame.
With the recent API changes, there are a few existing features which need to have thir API calls adjusted slightly.
Another feature that needs to be finished is displaying useful warnings and error messages.
While progress has been made on them and a reporting system has been built, messages still need to be fed into it.
Lastly, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response, alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
\subsection {Android}
So far, the only connection to the server that the android client has is when it
registers/logs in. We still need to connect the rest of the android client to
the server API to make sure all the communication between the android client
and the server are working. This includes joining public/private rounds,
competing in these rounds, and viewing leaderboards. While the UI is nearly
finished on the android client, nearly all of the connections to the servers
has yet to be done. Additionally, the android client needs to have more user
feedback and increased ability for the users to control which activity they
are in.
\subsection {Server}
Private game joining
Global leaderboard
